### 2016-02-01 text/MS.Rmd
few minor corrections and additions to text

In this model, different from the model in equation 2, the mass scaling slope is no longer allowed to vary across different species, but is still allowed to vary between different temperatures (1 $\times$ 2 = 2 parameters). The metabolic normalisation, however, is still allowed to vary across species (4 $\times$ 1 = 4 parameters) and between temperatures (1 additional parameters), and random effects were maintained (i.e. 3 hyper parameters). Equation 3 represents a statistical model nested in the model represented by equation 2, and therefore their performance can be directly assessed `r myCite('zuur2009book')`. Such comparison allowed us to formally test our main hypothesis of significant mass-temperature interactions across different species.

@@

The fact that $B_o$ and $\alpha$ covary in different ways depending on species and temperature (Figure 1) suggests that the metabolic costs of maintenance will vary for different species at different environmental temperatures. For example, *Bugula neritina* presented a shallower mass-scaling exponent at colder temperatures, possibly indicating that large cold-environment individuals are more efficient in spending energy than counterparts in warm environments. Thus, for this species, all else being equal, increases in temperature decrease the metabolic benefits of attaining a larger size while decreases in temperature reduce the metabolic normalisation. On the other hand, our results indicate that *Hippopodina* sp. presents a reduction in metabolic benefits of attaining a larger size at colder temperatures. Thus, for this encrusting species, one could predict that individuals living at higher temperatures should allocate more resources to attaining larger sizes (as opposed to reproduction, for instance) while individuals living at lower temperatures will be under less pressure to allocate resources to size. Importantly, though, we note that there are many extrinsic factors that may affect selection on body size (e.g. predation, competition, etc). Yet, such differentials in the costs and benefits of attaining large size may help explain why in species living in cold temperatures present a slower pace of life (e.g. `r myCite('rosa2010jmba')`). Moreover, they may represent necessary improvements on current attempts to scale up energy from individuals to higher levels of organisation (e.g. `r myCite(c('allen2005','yvondurocher2012b','barneche2014ele'))`).

@@

*Figure 1.* Estimates from the three-way interaction model as obtained by Bayesian methods in *JAGS*. Results for each species are represented in groups of four plots, with blue and red colours representing actual data and parameter estimates at 10 ˚C and 25 ˚C, respectively. *Top-left* and *bottom-right*: posterior probabilities of mass-scaling exponents and metabolic normalisations (respectively), with bars over curves representing 95% credible intervals, and numbers representing average estimates. *Bottom-left*: covariance between mass-scaling exponents and metabolic normalisations for each of the 6,000 MCMC iterations (translucent circles), with overlaid density heat-map. *Top-right*: regressions of individual metabolic rate, $\textrm{ln}B_i$, as functions of individual body mass, $\textrm{ln}M_i$. Regression fits were plotted using the average from the posterior distributions. In probability posterior plots (*top-left* and *bottom-right*), smooth probability curves (*n* = 511 values) were approximated from posterior density curves (*n* = 512 values); differences between adjacent $x$ values were multiplied by the average of adjacent $y$ values (i.e. $(x_{i+1} - x_{i}) \times ((y_{i+1} - y_{i})/2)$) thus insuring that the integral of the probability curve $\approx$ 1.

>>>>

In this model, different from the model in equation 2, the mass scaling slope is no longer allowed to vary across different species, but is still allowed to vary between different temperatures (1 $\times$ 2 = 2 parameters). The metabolic normalisation, however, is still allowed to vary across species (4 $\times$ 1 = 4 parameters) and between temperatures (1 additional parameter), and random effects were maintained (i.e. 3 hyper parameters). Equation 3 represents a statistical model nested in the model represented by equation 2, and therefore their performance can be directly assessed `r myCite('zuur2009book')`. Such comparison allowed us to formally test our main hypothesis of significant mass-temperature interactions across different species.

@@

The fact that $B_o$ and $\alpha$ covary in different ways depending on species and temperature (Figure 1) suggests that the metabolic costs of maintenance will vary for different species at different environmental temperatures. For example, *Bugula neritina* presented a shallower mass-scaling exponent at colder temperatures, possibly indicating that large cold-environment individuals are more efficient in spending energy than counterparts in warm environments. Thus, for this species, all else being equal, increases in temperature decrease the metabolic benefits of attaining a larger size while decreases in temperature reduce the metabolic normalisation. On the other hand, our results indicate that *Hippopodina* sp. presents a reduction in metabolic benefits of attaining a larger size at colder temperatures. Thus, for this encrusting species, one could predict that individuals living at higher temperatures should allocate more resources to attaining larger sizes (as opposed to reproduction, for instance) while individuals living at lower temperatures will be under less pressure to allocate resources to size. Importantly, though, we note that there are many extrinsic factors that may affect abundance and selection on body size (e.g. predation, competition, etc; `r myCite('barneche2016procb')`). Yet, such differentials in the costs and benefits of attaining large size may help explain why some species living in cold temperatures present a slower pace of life (e.g. `r myCite('rosa2010jmba')`). Moreover, they may represent necessary improvements on current attempts to scale up energy from individuals to higher levels of organisation (e.g. `r myCite(c('allen2005','yvondurocher2012b','barneche2014ele','barneche2016procb'))`).

@@

*Figure 1.* Estimates from the three-way interaction model as obtained by Bayesian methods in *JAGS*. Results for each species are represented in groups of four plots, with blue and red colours representing actual data and parameter estimates at 10 ˚C and 25 ˚C, respectively. *Top-left* and *bottom-right*: posterior probabilities of mass-scaling exponents and metabolic normalisations (respectively), with bars over curves representing 95% credible intervals, and numbers representing average estimates. *Bottom-left*: covariance between mass-scaling exponents and metabolic normalisations for each of the 6,000 MCMC iterations (translucent circles), with overlaid density heat-map. *Top-right*: regressions of individual metabolic rate, $\textrm{ln}B_i$, as functions of individual body mass, $\textrm{ln}M_i$. Regression fits were plotted using the average from the posterior distributions. In probability posterior plots (*top-left* and *bottom-right*), smooth probability curves (*n* = 511 values) were approximated from posterior probability density curves (*n* = 512 values); differences between adjacent $x$ values (i.e. parameter estimates) were multiplied by the average of adjacent $y$ values (i.e. respective probability density values; $(x_{i+1} - x_{i}) \times ((y_{i+1} - y_{i})/2)$) thus insuring that the integral of the probability curve $\approx$ 1.
